\documentclass[12pt]{article}
\usepackage{graphicx} % Required for inserting images
\usepackage[a4paper, total={6in, 9in}]{geometry}
\renewcommand{\thesection}{\hspace*{-1.0em}}
\renewcommand{\thesubsection}{\arabic{subsection}}

\title{Team Member Roles \& Responsibilities \\ (Nextra Morayfield Plaza \& Village News)}
\author{Connor McHugh}
\date{December 2023}

\begin{document}

\maketitle
\section{Core Roles \& Responsibilities}
These roles and resonsibilities are applicable to all team members.
\subsection{Personal Presentation}
\begin{itemize}
    \item \textbf{Punctuality:} You must be on the counter and ready to serve by the time that you are rostered to start. If you are running late please text or call the manager where practical.
    \item \textbf{Appearance:}
    \item \textbf{Mobile Phones:} Junior staff must have their phones in the back office unless it is needed for work purposes. Senior staff are welcome to have their phones with them.
\end{itemize}

\subsection{Customer Service}
\begin{itemize}
    \item \textbf{Connecting With Your Customer:} Great each customer with a smile, make eye contact, ask them about their day. Get to know regular customers and try to build a connection with them.
    \item \textbf{Processing Transactions Efficiently \& Accurately:}
    \item \textbf{Upselling \& Cross-Selling:} Upsell and cross-sell lotteries products to customers as directed.
    \item \textbf{Product Knowledge \& Locations:} Have an understanding of the products that we sell and their locations within the store. Have an understanding of the different lottery offerings that are available and the details of each offering.
\end{itemize}

\subsection{Counter Control}
\begin{itemize}
    \item \textbf{Counter Cleanliness:}
    \item \textbf{Restocking Consumables:} Ensure that all consumables (Paper \& plastic bags, terminal \& register rolls etc.) are stocked.
    \item \textbf{Instant Scratch-It's:} Ensure that the ISI dispenser/s are fully stocked and clean, and that the ISI draw has sufficient extra stock for at least two days worth of sales.
\end{itemize}

\subsection{Floor Management}
\begin{itemize}
    \item \textbf{Cards:} Both everyday and seasonal (when applicable) cards are to be kept neat and tidy. Seasonal cards are to be kept topped up when extra stock is available.
    \item \textbf{Floor Stands:} Keep floor stands topped up and faced, ensuring that 
    \item \textbf{Giftware:}
    \item \textbf{Stationery:}
\end{itemize}

\subsection{Store Opening}
\begin{itemize}
    \item 
\end{itemize}

\subsection{Store Closing}
\begin{itemize}
    \item 
\end{itemize}

\section{Additional Roles \& Responsibilities}
\subsection{Giftware Purchasing \& Management}

\subsection{Stationery Purchasing \& Management}

\subsection{Magazine Control}

\subsection{Newspaper Control}

\subsection{Lotteries Management}



\end{document}
